\documentclass[12pt, a4paper]{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % For Korean text
\usepackage{geometry}
\geometry{a4paper, margin=1in}

% Title
\title{Calculus - Chapter 10.2 Exercises}
\author{}
\date{}

\begin{document}
\maketitle
\hrulefill
\vspace{1em}

\subsection*{난이도 하}

\begin{enumerate}
    \item \textbf{Exercise 1:} Find $dy/dx$.
    \[ x = 2t^3+3t, \quad y = 4t - 5t^2 \]
    
    \item \textbf{Exercise 3:} Find $dy/dx$.
    \[ x = te^t, \quad y = t + \sin t \]
    
    \item \textbf{Exercise 7:} Find an equation of the tangent to the curve at the point corresponding to the given value of the parameter.
    \[ x = t^3+1, \quad y = t^4+t; \quad t = -1 \]
    
    \item \textbf{Exercise 10:} Find an equation of the tangent to the curve at the point corresponding to the given value of the parameter.
    \[ x = e^t \sin(\pi t), \quad y = e^{2t}; \quad t=0 \]
    
    \item \textbf{Exercise 5:} Find the slope of the tangent to the parametric curve at the indicated point.
    \[ x=t^2+2t, \quad y=2^t-2t; \quad (15, 2) \]
    
    \item \textbf{Exercise 35:} Find the area enclosed by the parametric curve and the x-axis.
    \[ x = t^3+1, \quad y = 2t - t^2 \]
    
    \item \textbf{Exercise 47:} Find the exact length of the curve.
    \[ x = \frac{2}{3}t^3, \quad y = t^2 - 2, \quad 0 \le t \le 3 \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 중}

\begin{enumerate}
    \setcounter{enumi}{7}
    \item \textbf{Exercise 13:} Find an equation of the tangent to the curve at the given point. Then graph the curve and the tangent.
    \[ x = t^2-t, \quad y = t^2+t+1; \quad (0,3) \]
    
    \item \textbf{Exercise 29:} Show that the curve $x = \cos t, y = \sin t \cos t$ has two tangents at $(0,0)$ and find their equations.
    
    \item \textbf{Exercise 15:} Find $dy/dx$ and $d^2y/dx^2$. For which values of $t$ is the curve concave upward?
    \[ x = t^2+1, \quad y = t^2+t \]
    
    \item \textbf{Exercise 17:} Find $dy/dx$ and $d^2y/dx^2$. For which values of $t$ is the curve concave upward?
    \[ x = e^t, \quad y = te^{-t} \]
    
    \item \textbf{Exercise 23:} Find the points on the curve where the tangent is horizontal or vertical.
    \[ x = \cos\theta, \quad y = \cos(3\theta) \]
    
    \item \textbf{Exercise 26:} Use a graph to estimate the coordinates of the lowest point and the leftmost point on the curve $x=t^4-2t, y=t+t^4$. Then find the exact coordinates.
    
    \item \textbf{Example 10.2.3:} Find the area under one arch of the cycloid $x = r(\theta - \sin\theta), y = r(1-\cos\theta)$.
    
    \item \textbf{Exercise 40:} Find the area of the region enclosed by the loop of the curve $x=1-t^2, y=t-t^3$.
    
    \item \textbf{Exercise 48:} Find the exact length of the curve.
    \[ x = e^t - t, \quad y = 4e^{t/2}, \quad 0 \le t \le 2 \]
    
    \item \textbf{Exercise 50:} Find the exact length of the curve.
    \[ x = 3\cos t - \cos(3t), \quad y = 3\sin t - \sin(3t), \quad 0 \le t \le \pi \]
    
    \item \textbf{Exercise 71:} Find the exact area of the surface obtained by rotating the given curve about the x-axis.
    \[ x=t^3, \quad y=t^2, \quad 0 \le t \le 1 \]
    
    \item \textbf{Exercise 75:} Find the surface area generated by rotating the given curve about the y-axis.
    \[ x=3t^2, \quad y=2t^3, \quad 0 \le t \le 5 \]
    
    \item \textbf{Exercise 55:} Find the distance traveled by a particle with position $(x, y)$ as $t$ varies in the given time interval. Compare with the length of the curve.
    \[ x = \sin^2 t, \quad y = \cos^2 t, \quad 0 \le t \le 3\pi \]
    
    \item \textbf{Exercise 57:} The parametric equations give the position (in meters) of a moving particle at time $t$ (in seconds). Find the speed of the particle at the indicated time.
    \[ x = 2t-3, \quad y = 2t^2-3t+6; \quad t=5 \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 상}

\begin{enumerate}
    \setcounter{enumi}{21}
    \item \textbf{Exercise 34:} Find equations of the tangents to the curve $x=3t^2+1, y=2t^3+1$ that pass through the point $(4,3)$.
    
    \item \textbf{Exercise 65:} Find the area of the region enclosed by the astroid $x=a\cos^3\theta, y=a\sin^3\theta$.
    
    \item \textbf{Exercise 52:} Graph the curve and find its exact length.
    \[ x = \cos t + \ln(\tan(t/2)), \quad y=\sin t, \quad \pi/4 \le t \le 3\pi/4 \]
    
    \item \textbf{Exercise 54:} Find the length of the loop of the curve $x=3t-t^3, y=3t^2$.
    
    \item \textbf{Exercise 73:} Find the exact area of the surface obtained by rotating the given curve about the x-axis.
    \[ x = a\cos^3\theta, \quad y=a\sin^3\theta, \quad 0 \le \theta \le \pi/2 \]
    
    \item \textbf{Exercise 79:} For a parametric curve $x=x(t), y=y(t)$, derive the formula for curvature $\kappa$:
    \[ \kappa(t) = \frac{|\dot{x}\ddot{y} - \dot{y}\ddot{x}|}{[\dot{x}^2 + \dot{y}^2]^{3/2}} \]
    where the dots indicate derivatives with respect to $t$.
    
    \item \textbf{Exercise 31b:} Show that if $d < r$, then the trochoid $x=r\theta - d\sin\theta, y=r-d\cos\theta$ does not have a vertical tangent.
\end{enumerate}

\end{document}
