\documentclass{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % 한국어 사용을 위한 패키지
\usepackage{geometry}
\geometry{a4paper, margin=1in} % 페이지 여백 설정

% Title
\title{Chapter 11.3 Exercises: The Integral Test and Estimation of Sums}
\author{James Stewart, Calculus, Metric Edition}
\date{}

\begin{document}
\maketitle
\hrulefill % 제목 아래 수평선
\vspace{1em} % 제목과 내용 사이 간격

% --- 난이도 하 (Easy) ---
\subsection*{Difficulty: Easy (6 Problems)}
\begin{enumerate}
    \item \textbf{Exercise 1:} Draw a picture to show that $\sum_{n=2}^{\infty} \dfrac{1}{n^{1.5}} < \int_{1}^{\infty} \dfrac{1}{x^{1.5}} dx$. What can you conclude about the series?
    \item \textbf{Exercise 3:} Use the Integral Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} n^{-3} \]
    \item \textbf{Exercise 5:} Use the Integral Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \dfrac{2}{5n-1} \]
    \item \textbf{Exercise 11:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n^{\sqrt{2}}} \]
    \item \textbf{Exercise 13:} Determine whether the series is convergent or divergent.
    \[ 1 + \dfrac{1}{8} + \dfrac{1}{27} + \dfrac{1}{64} + \dfrac{1}{125} + \dots \]
    \item \textbf{Exercise 21:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n^2 + 4} \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 중 (Medium) ---
\subsection*{Difficulty: Medium (11 Problems)}
\begin{enumerate}
    \setcounter{enumi}{6} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 7:} Use the Integral Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=2}^{\infty} \dfrac{n^2}{n^3+1} \]
    \item \textbf{Exercise 8:} Use the Integral Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} n^2 e^{-n^3} \]
    \item \textbf{Exercise 9:} Use the Integral Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=2}^{\infty} \dfrac{1}{n(\ln n)^3} \]
    \item \textbf{Exercise 17:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \dfrac{\sqrt{n}+4}{n^2} \]
    \item \textbf{Exercise 23:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=2}^{\infty} \dfrac{1}{n \ln n} \]
    \item \textbf{Exercise 24:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=2}^{\infty} \dfrac{\ln n}{n^2} \]
    \item \textbf{Exercise 25:} Determine whether the series is convergent or divergent.
    \[ \sum_{k=1}^{\infty} k e^{-k} \]
    \item \textbf{Exercise 27:} Determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n^2 + n^3} \]
    \item \textbf{Exercise 38(a):} Find the partial sum $s_{10}$ of the series $\sum_{n=1}^{\infty} 1/n^4$. Estimate the error in using $s_{10}$ as an approximation to the sum of the series.
    \item \textbf{Exercise 39(a):} Use the sum of the first 10 terms to estimate the sum of the series $\sum_{n=1}^{\infty} 1/n^2$. How good is this estimate?
    \item \textbf{Exercise 40:} Find the sum of the series $\sum_{n=1}^{\infty} n e^{-2n}$ correct to four decimal places.
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 상 (Hard) ---
\subsection*{Difficulty: Hard (5 Problems)}
\begin{enumerate}
    \setcounter{enumi}{17} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 31:} Find the values of $p$ for which the series $\sum_{n=2}^{\infty} \dfrac{1}{n(\ln n)^p}$ is convergent.
    \item \textbf{Exercise 32:} Find the values of $p$ for which the series $\sum_{n=3}^{\infty} \dfrac{1}{n \ln n [\ln(\ln n)]^p}$ is convergent.
    \item \textbf{Exercise 33:} Find the values of $p$ for which the series $\sum_{n=1}^{\infty} n (1+n^2)^p$ is convergent.
    \item \textbf{Exercise 47:} Find all positive values of $b$ for which the series $\sum_{n=1}^{\infty} b^{\ln n}$ converges.
    \item \textbf{Exercise 48:} Find all values of $c$ for which the following series converges: $\sum_{n=1}^{\infty} (\dfrac{c}{n} - \dfrac{1}{n+1})$.
\end{enumerate}

\end{document}