\documentclass[12pt, a4paper]{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

% Title
\title{Chapter 11.4 Exercises: The Comparison Tests}
\author{James Stewart, Calculus, Metric Edition}
\date{}

\begin{document}
\maketitle
\hrulefill
\vspace{1em}

\subsection*{Difficulty: Easy}
\begin{enumerate}
    \item \textbf{Exercise 3:} Use the Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n^2 + n + 1} \]

    \item \textbf{Exercise 5:} Use the Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{5}{2 + 3^n} \]

    \item \textbf{Exercise 7:} Use the Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=2}^{\infty} \dfrac{n^3}{n^4 - 1} \]
    
    \item \textbf{Exercise 9:} Use the Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n}{n^3 + 1} \]

    \item \textbf{Exercise 11:} Use the Limit Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n+1}{n\sqrt{n}} \]

    \item \textbf{Exercise 13:} Use the Limit Comparison Test to determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n-1}{n^2\sqrt{n}} \]
    
    \item \textbf{Exercise 15:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n+2}{(n+1)^3} \]
    
    \item \textbf{Exercise 17:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{3 + \cos n}{3^n} \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{Difficulty: Medium}
\begin{enumerate}
    \setcounter{enumi}{8}
    \item \textbf{Exercise 19:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{2n^2 + 7n}{3^n (n^2 + 5n - 1)} \]

    \item \textbf{Exercise 20:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \left( 1 + \dfrac{1}{n} \right)^2 e^{-n} \]
    
    \item \textbf{Exercise 21:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{\sqrt{n^2 + 1}} \]

    \item \textbf{Exercise 23:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n!}{(n+2)!} \]
    
    \item \textbf{Exercise 25:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n^2 + n + 1}{n^4 + n^2} \]
    
    \item \textbf{Exercise 26:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{\sqrt{n^4 + 1}}{n^3 + n^2} \]

    \item \textbf{Exercise 27:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{1+2^n}{1+3^n} \]
    
    \item \textbf{Exercise 29:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{n+1}{n 2^n} \]
    
    \item \textbf{Exercise 31:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \sin\left(\dfrac{1}{n}\right) \]
    
    \item \textbf{Exercise 32:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n^{1+1/n}} \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{Difficulty: Hard}
\begin{enumerate}
    \setcounter{enumi}{18}
    \item \textbf{Exercise 35:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{n!} \]
    
    \item \textbf{Exercise 37:} Use the sum of the first 10 terms to approximate the sum of the series. Estimate the error.
    \[ \sum_{n=1}^{\infty} \dfrac{1}{1 + 2^n} \]

    \item \textbf{Exercise 39:} For which values of $p$ does the series $\sum_{n=2}^{\infty} \dfrac{1}{n^p \ln n}$ converge?
    
    \item \textbf{Exercise 40:} If $a_n > 0$ and $\sum a_n$ converges, show that $\sum \ln(1+a_n)$ also converges.

    \item \textbf{Exercise 41:} If $a_n > 0$ and $\sum a_n$ converges, show that $\sum (a_n / n)$ also converges.

    \item \textbf{Exercise 43:} (a) Suppose that $\sum a_n$ and $\sum b_n$ are series with positive terms and $\sum b_n$ is convergent. Prove that if $\lim_{n \to \infty} \dfrac{a_n}{b_n} = 0$, then $\sum a_n$ is also convergent.
    
    \item \textbf{Exercise 44:} (a) Suppose that $\sum a_n$ and $\sum b_n$ are series with positive terms and $\sum b_n$ is divergent. Prove that if $\lim_{n \to \infty} \dfrac{a_n}{b_n} = \infty$, then $\sum a_n$ is also divergent.
\end{enumerate}

\end{document}
