\documentclass[12pt, a4paper]{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % For Korean text
\usepackage{geometry}
\geometry{a4paper, margin=1in}

% Title
\title{Calculus - Chapter 9.5 Representative Exercises (Linear Equations)}
\author{}
\date{}

\begin{document}
\maketitle
\hrulefill
\vspace{1em}

\subsection*{난이도 하}
\begin{enumerate}
    \item \textbf{Exercise 2:} Determine whether the differential equation is linear. If it is linear, then write it in the form of Equation 1.
    \[ y' - x = y \tan x \]

    \item \textbf{Exercise 5:} Solve the differential equation.
    \[ y' + y = 1 \]

    \item \textbf{Exercise 6:} Solve the differential equation.
    \[ y' - y = e^x \]

    \item \textbf{Exercise 7:} Solve the differential equation.
    \[ y' = x - y \]

    \item \textbf{Exercise 17:} Solve the initial-value problem.
    \[ xy' + y = 3x^2, \quad y(1)=4 \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 중 }
\begin{enumerate}
    \setcounter{enumi}{5} % Continue numbering
    \item \textbf{Exercise 9:} Solve the differential equation.
    \[ xy' + y = \sqrt{x} \]

    \item \textbf{Exercise 12:} Solve the differential equation.
    \[ y' - 3x^2y = x^2 \]

    \item \textbf{Exercise 13:} Solve the differential equation.
    \[ t^2\frac{dy}{dt} + 3ty = \sqrt{1+t^2}, \quad t>0 \]

    \item \textbf{Exercise 19:} Solve the initial-value problem.
    \[ x^2y' + 2xy = \ln x, \quad y(1)=2 \]

    \item \textbf{Exercise 21:} Solve the initial-value problem.
    \[ t\frac{du}{dt} = t^2 + 3u, \quad t>0, u(2)=4 \]

    \item \textbf{Exercise 23:} Solve the initial-value problem.
    \[ xy' = y + x^2\sin x, \quad y(\pi)=0 \]

    \item \textbf{Exercise 31:} In the circuit shown in Figure 4, a battery supplies a constant voltage of 40 V, the inductance is 2 H, the resistance is 10 $\Omega$, and $I(0)=0$.
    \begin{itemize}
        \item[(a)] Find $I(t)$.
        \item[(b)] Find the current after 0.1 seconds.
    \end{itemize}

    \item \textbf{Exercise 33:} For the given RC circuit, find the charge and the current at time t. (Given: $R=5\Omega$, $C=0.05$ F, $E(t)=60$ V, $Q(0)=0$ C)

    \item \textbf{Exercise 35:} Solve the learning curve differential equation {\large$\frac{dP}{dt}$}$=k[M-P(t)]$ as a linear differential equation.

    \item \textbf{Exercise 39(a):} An object with mass m is dropped from rest, and air resistance is proportional to the speed, giving the DE $m\frac{dv}{dt}=mg-cv$.
    \begin{itemize}
        \item[(a)] Solve this as a linear equation to show that $v=\frac{mg}{c}(1-e^{-ct/m})$.
    \end{itemize}
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 상}
\begin{enumerate}
    \setcounter{enumi}{15} % Continue numbering
    \item \textbf{Exercise 28:} Solve the Bernoulli differential equation $xy' + y = -xy^2$.

    \item \textbf{Exercise 29:} Solve the Bernoulli differential equation $y' + \frac{2}{x}y = \frac{y^3}{x^2}$.

    \item \textbf{Exercise 32:} In the circuit in Figure 4, a generator supplies $E(t)=40 \sin 60t$ V, the inductance is 1 H, the resistance is 20 $\Omega$, and $I(0)=1$ A.
    \begin{itemize}
        \item[(a)] Find $I(t)$.
        \item[(b)] Find the current after 0.1 seconds.
    \end{itemize}

    \item \textbf{Exercise 37:} A tank contains 100 L of water. A solution with concentration 0.4 kg/L is added at 5 L/min. The mixed solution is drained at 3 L/min. Show that y (amount of salt) satisfies $\frac{dy}{dt}=2-\frac{3y}{100+2t}$. Solve this equation.

    \item \textbf{Exercise 41:}
    \begin{itemize}
        \item[(a)] Show that the substitution $z=1/P$ transforms the logistic DE $P'=kP(1-P/M)$ into the linear DE $z'+kz=\frac{k}{M}$.
        \item[(b)] Solve the linear DE in part (a) to obtain an expression for $P(t)$.
    \end{itemize}
\end{enumerate}

\end{document}
