\documentclass{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % 한국어 사용을 위한 패키지
\usepackage{geometry}
\geometry{a4paper, margin=1in} % 페이지 여백 설정

% Title
\title{Chapter 11.4 Exercises: The Comparison Tests}
\author{James Stewart, Calculus, Metric Edition}
\date{}

\begin{document}
\maketitle
\hrulefill % 제목 아래 수평선
\vspace{1em} % 제목과 내용 사이 간격

% --- 난이도 하 (Easy) ---
\subsection*{Difficulty: Easy (6 Problems)}
\begin{enumerate}
    \item \textbf{Exercise 7:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1}{n^3 + 8} \]
    \item \textbf{Exercise 8:} Determine whether the series converges or diverges.
    \[ \sum_{n=2}^{\infty} \frac{1}{\sqrt{n}-1} \]
    \item \textbf{Exercise 9:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n+1}{n\sqrt{n}} \]
    \item \textbf{Exercise 11:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{9^n}{3+10^n} \]
    \item \textbf{Exercise 12:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{6^n}{5^n-1} \]
    \item \textbf{Exercise 18:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1}{\sqrt[3]{3n^4+1}} \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 중 (Medium) ---
\subsection*{Difficulty: Medium (13 Problems)}
\begin{enumerate}
    \setcounter{enumi}{6} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 10:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n-1}{n^3+1} \]
    \item \textbf{Exercise 15:} Determine whether the series converges or diverges.
    \[ \sum_{k=1}^{\infty} \frac{\sqrt[3]{k}}{\sqrt{k^3+4k+3}} \]
    \item \textbf{Exercise 16:} Determine whether the series converges or diverges.
    \[ \sum_{k=1}^{\infty} \frac{(2k-1)(k^2-1)}{(k+1)(k^2+4)^2} \]
    \item \textbf{Exercise 19:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{4^{n+1}}{3^n-2} \]
    \item \textbf{Exercise 21:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1}{\sqrt{n^2+1}} \]
    \item \textbf{Exercise 22:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{2}{\sqrt{n}+2} \]
    \item \textbf{Exercise 23:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n+1}{n^3+n} \]
    \item \textbf{Exercise 24:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n^2+n+1}{n^4+n^2} \]
    \item \textbf{Exercise 28:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n+3^n}{n+2^n} \]
    \item \textbf{Exercise 29:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{e^n+1}{ne^n+1} \]
    \item \textbf{Exercise 31:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{2+\sin n}{n^2} \]
    \item \textbf{Exercise 33:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} (1+\frac{1}{n})^2 e^{-n} \]
    \item \textbf{Exercise 41:} Use the sum of the first 10 terms to approximate the sum of the series $\sum_{n=1}^{\infty} \frac{1}{5+n^5}$. Estimate the error.
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 상 (Hard) ---
\subsection*{Difficulty: Hard (6 Problems)}
\begin{enumerate}
    \setcounter{enumi}{19} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 17:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1+\cos n}{e^n} \]
    \item \textbf{Exercise 34:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{e^{1/n}}{n} \]
    \item \textbf{Exercise 35:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1}{n!} \]
    \item \textbf{Exercise 36:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{n!}{n^n} \]
    \item \textbf{Exercise 37:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \sin(\frac{1}{n}) \]
    \item \textbf{Exercise 40:} Determine whether the series converges or diverges.
    \[ \sum_{n=1}^{\infty} \frac{1}{n^{1+1/n}} \]
    \item \textbf{Exercise 48:}
    (a) Suppose that $\sum a_n$ and $\sum b_n$ are series with positive terms and $\sum b_n$ is convergent. Prove that if
    \[ \lim_{n \to \infty} \frac{a_n}{b_n} = 0 \]
    then $\sum a_n$ is also convergent.\\
    (b) Use part (a) to show that the series converges.
    \[ \text{(i) } \sum_{n=1}^{\infty} \frac{\ln n}{n^3} \qquad \text{(ii) } \sum_{n=1}^{\infty} \left(1 - \cos \frac{1}{n^2}\right) \]

    \item \textbf{Exercise 49:}
    (a) Suppose that $\sum a_n$ and $\sum b_n$ are series with positive terms and $\sum b_n$ is divergent. Prove that if
    \[ \lim_{n \to \infty} \frac{a_n}{b_n} = \infty \]
    then $\sum a_n$ is also divergent.\\
    (b) Use part (a) to show that the series diverges.
    \[ \text{(i) } \sum_{n=2}^{\infty} \frac{1}{\ln n} \qquad \text{(ii) } \sum_{n=1}^{\infty} \frac{\ln n}{n} \]

    \item \textbf{Exercise 50:} Give an example of a pair of series $\sum a_n$ and $\sum b_n$ with positive terms where $\lim_{n \to \infty} (a_n / b_n) = 0$ and $\sum b_n$ diverges, but $\sum a_n$ converges. (Compare with Exercise 48.)

    \item \textbf{Exercise 55:} Let $\sum a_n$ and $\sum b_n$ be series with positive terms. Is each of the following statements true or false? If the statement is false, give an example that disproves the statement.
    \begin{enumerate}
        \item[(a)] If $\sum a_n$ and $\sum b_n$ are divergent, then $\sum a_n b_n$ is divergent.
        \item[(b)] If $\sum a_n$ converges and $\sum b_n$ diverges, then $\sum a_n b_n$ diverges.
        \item[(c)] If $\sum a_n$ and $\sum b_n$ are convergent, then $\sum a_n b_n$ is convergent.
    \end{enumerate}
\end{enumerate}

\end{document}