\documentclass{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % 한국어 사용을 위한 패키지
\usepackage{geometry}
\geometry{a4paper, margin=1in} % 페이지 여백 설정

% Title
\title{Chapter 11.5 Exercises: Alternating Series and Absolute Convergence}
\author{James Stewart, Calculus, Metric Edition}
\date{}

\begin{document}
\maketitle
\hrulefill % 제목 아래 수평선
\vspace{1em} % 제목과 내용 사이 간격

% --- 난이도 하 (Easy) ---
\subsection*{Difficulty: Easy (6 Problems)}
\begin{enumerate}
    \item \textbf{Exercise 2:} Test the series for convergence or divergence.
    \[ \frac{2}{3} - \frac{2}{5} + \frac{2}{7} - \frac{2}{9} + \frac{2}{11} - \dots \]
    
    \item \textbf{Exercise 3:} Test the series for convergence or divergence.
    \[ -\frac{2}{5} + \frac{4}{6} - \frac{6}{7} + \frac{8}{8} - \frac{10}{9} + \dots \]
    
    \item \textbf{Exercise 5:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^{n-1}}{3+5n} \]
    
    \item \textbf{Exercise 6:} Test the series for convergence or divergence.
    \[ \sum_{n=0}^{\infty} \frac{(-1)^{n+1}}{\sqrt{n}+1} \]
    
    \item \textbf{Exercise 22:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^n}{n^4} \]
    
    \item \textbf{Exercise 23:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^{n-1}}{n^{2/3}} \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 중 (Medium) ---
\subsection*{Difficulty: Medium (11 Problems)}
\begin{enumerate}
    \setcounter{enumi}{6} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 7:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^n \frac{3n-1}{2n+1} \]
    
    \item \textbf{Exercise 9:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^n e^{-n} \]
    
    \item \textbf{Exercise 10:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^n \frac{\sqrt{n}}{2n+3} \]
    
    \item \textbf{Exercise 11:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^{n+1} \frac{n^2}{n^3+4} \]
    
    \item \textbf{Exercise 14:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^{n-1} \arctan n \]
    
    \item \textbf{Exercise 24:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=0}^{\infty} \frac{(-1)^{n+1} n^2}{n^2+1} \]
    
    \item \textbf{Exercise 27:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{\sin n}{2^n} \]
    
    \item \textbf{Exercise 30:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^{n-1} n}{n^2+4} \]
    
    \item \textbf{Exercise 32:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^n n}{\sqrt{n^3+2}} \]
    
    \item \textbf{Exercise 37:} Show that the series is convergent. How many terms of the series do we need to add in order to find the sum to the indicated accuracy?
    \[ \sum_{n=1}^{\infty} \frac{(-1)^{n+1}}{n^6} \quad (|\text{error}| < 0.00005) \]
    
    \item \textbf{Exercise 41:} Approximate the sum of the series correct to four decimal places.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^n}{(2n)!} \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 상 (Hard) ---
\subsection*{Difficulty: Hard (5 Problems)}
\begin{enumerate}
    \setcounter{enumi}{17} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 17:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^n \sin\left(\frac{\pi}{n}\right) \]
    
    \item \textbf{Exercise 18:} Test the series for convergence or divergence.
    \[ \sum_{n=1}^{\infty} (-1)^n \cos\left(\frac{\pi}{n}\right) \]
    
    \item \textbf{Exercise 29:} Determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{1+2\sin n}{n^3} \]
    
    \item \textbf{Exercise 46:} For what values of $p$ is the following series convergent?
    \[ \sum_{n=1}^{\infty} \frac{(-1)^{n-1}}{n^p} \]
    
    \item \textbf{Exercise 53:} Suppose the series $\sum a_n$ is conditionally convergent.
    \begin{enumerate}
        \item[(a)] Prove that the series $\sum n^2 a_n$ is divergent.
        \item[(b)] Conditional convergence of $\sum a_n$ is not enough to determine whether $\sum n a_n$ is convergent. Show this by giving an example of a conditionally convergent series such that $\sum n a_n$ converges and an example where $\sum n a_n$ diverges.
    \end{enumerate}
\end{enumerate}

\end{document}