\documentclass{article}

% Required Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{kotex} % 한국어 사용을 위한 패키지
\usepackage{geometry}
\geometry{a4paper, margin=1in} % 페이지 여백 설정

% Title
\title{Chapter 11.6 Exercises: The Ratio and Root Tests}
\author{James Stewart, Calculus, Metric Edition}
\date{}

\begin{document}
\maketitle
\hrulefill % 제목 아래 수평선
\vspace{1em} % 제목과 내용 사이 간격

% --- 난이도 하 (Easy) ---
\subsection*{Difficulty: Easy (5 Problems)}
\begin{enumerate}
    \item \textbf{Exercise 3:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{n}{5^n} \]
    
    \item \textbf{Exercise 4:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-2)^n}{n^2} \]
    
    \item \textbf{Exercise 7:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{k=1}^{\infty} \frac{1}{k!} \]
    
    \item \textbf{Exercise 8:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{k=1}^{\infty} k e^{-k} \]
    
    \item \textbf{Exercise 21:} Use the Root Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \left(\frac{n^2+1}{2n^2+1}\right)^n \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 중 (Medium) ---
\subsection*{Difficulty: Medium (10 Problems)}
\begin{enumerate}
    \setcounter{enumi}{5} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 9:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{10^n}{(n+1) 4^{2n+1}} \]
    
    \item \textbf{Exercise 10:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{n!}{100^n} \]
    
    \item \textbf{Exercise 12:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{n^{10}}{(-10)^{n+1}} \]
    
    \item \textbf{Exercise 13:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{\cos(n\pi/3)}{n!} \]
    
    \item \textbf{Exercise 22:} Use the Root Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-2)^n}{n^n} \]
    
    \item \textbf{Exercise 24:} Use the Root Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \left(\frac{-2n}{n+1}\right)^{5n} \]
    
    \item \textbf{Exercise 25:} Use the Root Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \left(1 + \frac{1}{n}\right)^{n^2} \]
    
    \item \textbf{Exercise 27:} Use any test to determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=2}^{\infty} \frac{(-1)^n \ln n}{n} \]
    
    \item \textbf{Exercise 31:} Use any test to determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} (\frac{n}{\ln{n}})^n \]
    
    \item \textbf{Exercise 33:} Use any test to determine whether the series is absolutely convergent, conditionally convergent, or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(-1)^n \arctan n}{n^2} \]
\end{enumerate}

\hrulefill
\vspace{1em}

% --- 난이도 상 (Hard) ---
\subsection*{Difficulty: Hard (5 Problems)}
\begin{enumerate}
    \setcounter{enumi}{15} % 이전 목록 번호 이어서 시작
    \item \textbf{Exercise 14:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{n!}{n^n} \]
    
    \item \textbf{Exercise 16:} Use the Ratio Test to determine whether the series is convergent or divergent.
    \[ \sum_{n=1}^{\infty} \frac{(2n)!}{(n!)^2} \]
    
    \item \textbf{Exercise 35:} The terms of a series are defined recursively by the equations
    \[ a_1 = 2 \qquad a_{n+1} = \frac{5n+1}{4n+3} a_n \]
    Determine whether $\sum a_n$ converges or diverges.
    
    \item \textbf{Exercise 40:} For which positive integers $k$ is the following series convergent?
    \[ \sum_{n=1}^{\infty} \frac{(n!)^2}{(kn)!} \]
    
    \item \textbf{Exercise 42:} Let $\sum a_n$ be a series with positive terms and let $r_n = a_{n+1}/a_n$. Suppose that $\lim_{n \to \infty} r_n = L < 1$, so $\sum a_n$ converges by the Ratio Test. As usual, we let $R_n$ be the remainder after $n$ terms, that is,
    \[ R_n = a_{n+1} + a_{n+2} + a_{n+3} + \dots \]
    \begin{enumerate}
        \item[(a)] If $\{r_n\}$ is a decreasing sequence and $r_{n+1} < 1$, show, by summing a geometric series, that
        \[ R_n \le \frac{a_{n+1}}{1-r_{n+1}} \]
        \item[(b)] If $\{r_n\}$ is an increasing sequence, show that
        \[ R_n \le \frac{a_{n+1}}{1-L} \]
    \end{enumerate}
\end{enumerate}

\end{document}