\documentclass[12pt, a4paper]{article}

% Required Packages
\usepackage{amsmath, amssymb, graphicx}
\usepackage{kotex} % For Korean text
\usepackage{geometry}
\geometry{a4paper, margin=1in}

% Title
\title{Calculus - Chapter 9.3 Representative Exercises (Separable Equations)}

\begin{document}
\maketitle
\hrulefill
\vspace{1em}

\subsection*{난이도 하}
\begin{enumerate}
    \item \textbf{Exercise 1:} Solve the differential equation.
    \[ \frac{dy}{dx} = 3x^2y^2 \]

    \item \textbf{Exercise 3:} Solve the differential equation.
    \[ \frac{dy}{dx} = x\sqrt{y} \]

    \item \textbf{Exercise 8:} Solve the differential equation.
    \[ \frac{dy}{dx} = 2x(y^2 + 1) \]

    \item \textbf{Exercise 13:} Find the solution of the differential equation that satisfies the given initial condition.
    \[ \frac{dy}{dx} = xe^y, \quad y(0)=0 \]

    \item \textbf{Exercise 14:} Find the solution of the differential equation that satisfies the given initial condition.
    \[\frac{dP}{dt} = \sqrt{Pt}, \quad P(1)=2 \]
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 중}
\begin{enumerate}
    \setcounter{enumi}{5} % Continue numbering
    \item \textbf{Exercise 9:} Solve the differential equation.
    \[ \frac{dp}{dt} = t^2p - p + t^2 - 1 \]

    \item \textbf{Exercise 10:} Solve the differential equation.
    \[ \frac{dz}{dt} + e^{t+z} = 0 \]

    \item \textbf{Exercise 18:} Find the solution of the differential equation that satisfies the given initial condition.
    \[ x + 3y^2\sqrt{x^2+1}\frac{dy}{dx} = 0, \quad y(0)=1 \]

    \item \textbf{Exercise 20:} Find the solution of the differential equation that satisfies the given initial condition.
    \[ \frac{dy}{dx} = \frac{x \sin x}{y}, \quad y(0)=-1 \]

    \item \textbf{Exercise 21:} Find an equation of the curve that passes through the point (0, 2) and whose slope at $(x,y)$ is $x/y$.

    \item \textbf{Exercise 33:} Find the orthogonal trajectories of the family of curves.
    \[ y = \frac{k}{x} \]

    \item \textbf{Exercise 39:} Solve the initial-value problem in Exercise 9.2.27 to find an expression for the charge at time t. Find the limiting value of the charge.

    \item \textbf{Exercise 40:} Solve the differential equation that models the temperature of a $95^{\circ}\text{C}$ cup of coffee in a $20^{\circ}\text{C}$ room.

    \item \textbf{Exercise 41:} Solve the differential equation for the learning model $\frac{dP}{dt}=k(M-P)$.

    \item \textbf{Exercise 47:} A tank contains 1000 L of brine with 15 kg of dissolved salt. Pure water enters the tank at a rate of 10 L/min. The solution is kept thoroughly mixed and drains from the tank at the same rate. How much salt is in the tank (a) after t minutes and (b) after 20 minutes?
\end{enumerate}

\hrulefill
\vspace{1em}

\subsection*{난이도 상}
\begin{enumerate}
    \setcounter{enumi}{15} % Continue numbering
    \item \textbf{Exercise 23:} Solve the differential equation $y' = x+y$ by making the change of variable $u=x+y$.

    \item \textbf{Exercise 31:} Find the orthogonal trajectories of the family of curves.
    \[ x^2 + 2y^2 = k^2 \]

    \item \textbf{Exercise 32:} Find the orthogonal trajectories of the family of curves.
    \[ y^2 = kx^3 \]

    \item \textbf{Exercise 42:} In an elementary chemical reaction, $A+B \rightarrow C$. The law of mass action states that $\frac{dx}{dt} = k(a-x)(b-x)$.
    \begin{itemize}
        \item[(a)] Assuming that $a \neq b$, find x as a function of t. Use the fact that the initial concentration of C is 0.
        \item[(b)] Find $x(t)$ assuming that $a=b$.
    \end{itemize}

    \item \textbf{Exercise 52(a):} An object of mass m is moving horizontally through a medium which resists the motion with a force $m\frac{dv}{dt}=f(v)$.
    \begin{itemize}
        \item[(a)] Suppose that the resisting force is proportional to the velocity, $f(v)=-kv$. Let $v(0)=v_0$ and $s(0)=s_0$. Determine v and s at any time t. What is the total distance that the object travels from time $t=0$?
    \end{itemize}
\end{enumerate}

\end{document}
